### 2016-11-04 introduction.tex
more shit

\section{Introduction \& Literature Review}\label{sec1}

Pruning algorithms, as comprehensively surveyed by \cite{reed1993pruning}, are a useful set of heuristics designed to identify and remove elements from a neural network which are either redundant or do not significantly contribute to the output of the network. This is motivated by the observed tendency of neural networks to over-fit to the idiosyncrasies of their training data given too many trainable parameters or too few input patterns from which to generalize, as stated by \cite{chauvin1990generalization}.

Network architecture design and hyperparameter selection are inherently difficult tasks typically approached using a few well-known rules of thumb, e.g. various weight initialization procedures, choosing the width and number of layers, different activation functions, learning rates, momentum, etc. Some of this ``black art'' appears unavoidable. For problems which cannot be solved using linear threshold units alone, \cite{baum1989size} demonstrate that there is no way to precisely determine the appropriate size of a neural network a priori given any random set of training instances. Using too few neurons seems to inhibit learning, and so in practice it is common to attempt to over-parameterize networks initially using a large number of hidden units and weights, and then prune them afterwards if necessary. Of course, as the old saying goes, there's more than one way to skin a neural network.

@@

The generalization performance of neural networks has been well studied, and apart from pruning algorithms many heuristics have been used to avoid overfitting, such as dropout (\cite{srivastava2014dropout}), maxout (\cite{goodfellow2013maxout}), and cascade correlation (\cite{fahlman1989cascade}), among others. Of course, while cascade correlation specifically tries to construct of minimal networks, many techniques to improve network generalization do not explicitly attempt to reduce the total number of parameters or the memory footprint of a trained network per se.

>>>>

\section{Introduction}\label{sec1}

In this work we propose and evaluate a novel algorithm for pruning whole neurons from a trained neural network without any re-training and examine its performance compared to simpler methods. We then analyze the kinds of errors made by our algorithm and use this to launch an investigation into the fundamental nature of learning representations in neural networks. We find that our results corroborate a seemingly forgotten 27-year old observation by \cite{mozer1989skeletonization} concerning the nature of neural network learning.

\section{Literature Review}
Pruning algorithms, as comprehensively surveyed by \cite{reed1993pruning}, are a useful set of heuristics designed to identify and remove elements from a neural network which are either redundant or do not significantly contribute to the output of the network. This is motivated by the observed tendency of neural networks to overfit to the idiosyncrasies of their training data given too many trainable parameters or too few input patterns from which to generalize, as stated by \cite{chauvin1990generalization}.

Network architecture design and hyperparameter selection are inherently difficult tasks typically approached using a few well-known rules of thumb, e.g. various weight initialization procedures, choosing the width and number of layers, different activation functions, learning rates, momentum, etc. Some of this ``black art'' appears unavoidable. For problems which cannot be solved using linear threshold units alone, \cite{baum1989size} demonstrate that there is no way to precisely determine the appropriate size of a neural network a priori given any random set of training instances. Using too few neurons seems to inhibit learning, and so in practice it is common to attempt to over-parameterize networks initially using a large number of hidden units and weights, and then prune or compress them afterwards if necessary. Of course, as the old saying goes, there's more than one way to skin a neural network.

@@

The generalization behavior of neural networks has been well studied, and apart from pruning algorithms many heuristics have been used to avoid overfitting, such as dropout (\cite{srivastava2014dropout}), maxout (\cite{goodfellow2013maxout}), and cascade correlation (\cite{fahlman1989cascade}), among others. Of course, while cascade correlation specifically tries to construct of minimal networks, many techniques to improve network generalization do not explicitly attempt to reduce the total number of parameters or the memory footprint of a trained network per se.
